AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
polished sect 2

Targeting geographical distance, Carmel~\cite{carmel2001} suggests a
tactic to reduce intensive collaboration. His approach divides the
whole software life-cycle on levels of complexity. Each level has a
degree of collaboration. For example, some developers working on a
project with high collaboration level should use the follow-the-sun
approach: when concluding the work day, they pass their work to the
team working on another time-zone. Other tactics are suggested by the
same author to deal with the three distances, like separating foreign
units of developers in time-zone bands.

Battin et al.~\cite{battin2001} propose and argues about their
experiments using specific methodologies created for the distributed
development centers of the Motorola Company (which has over 25
software development centers worldwide). These methodologies included
constant communication with critical units, incremental integration
and scheduled based on time-zones distributed to developers on 6
countries from 3 continents.

While considering free software projects instead of companies, the
same factors are present and some methodologies
arises. German~\cite{german2003} gives a concise review of
methodologies used by the GNOME project, one of the most active free
software projects and used by companies like Sun Microsystems. It is
interesting to note a difference on viewpoint present on his paper:
German focuses the methodology description on code. He start explaining
that GNOME is separated into modules (76 on version 2.4, to be
precise) and each module has one maintainer who divide his modules
into separated parts in which other developers can work on independent
tasks, along other responsibilities. As like others free software
projects, all the development was done using a \emph{bugtracker} to
bugs and issues management, mail lists and Internet Relay Chat (IRC)
to discussion and communication and a software configuration
management like SVN or Git. Periodical (commonly yearly) conferences
like GUADEC is common on free and open source projects to face-to-face
meeting and is based each time on a different place.

>>>>

Targeting geographical distance, Carmel~\cite{carmel2001} suggests a
strategy to reduce intensive collaboration. His approach divides the
whole software life-cycle into levels of complexity. Each level has a
degree of collaboration. For example, some developers working on a
project with high collaboration level should use the follow-the-sun
approach: when concluding the work day, they pass their work to the
team working on another time-zone. Other tactics are suggested by the
same author to deal with the three distances, such as separating foreign
units of developers in time-zone bands.

Battin~\etal~\cite{battin2001} propose and discuss their
experiments using specific methodologies created for the distributed
development centers from Motorola (at the time having 25+
software development centers worldwide). These methodologies included
constant communication with critical units, incremental integration
and schedules based on time-zones distributed to developers on 6
countries from 3 continents.

In considering free software projects instead of companies,
similar factors are present and specialized methodologies
arise. German~\cite{german2003} provides a concise review of
the methodologies used by the GNOME project, one of the most active of all free
software projects. The manuscript is centered on the software architecture. It
begins by explaining that GNOME is separated into modules (76 on version 2.4, to be
precise) and each module has one maintainer who divides his modules into
separate parts in which other developers can work on independent tasks, along
other responsibilities. As in other free software projects, all 
development was done using a \emph{bugtracker} for bug and issue management,
mail lists and Internet Relay Chat (IRC) for discussion and communication and a
version control system like Git or Mercurial. Periodical (commonly yearly)
conferences like GUADEC is common on free and open source projects for
face-to-face meetings and is based on a different place each time.
